# Another knitr Document
Jessica Bohning

## Introduction

This is some text (i.e. a "text chunk"). Here is a code chunk.
```{r simulation, echo=FALSE}
## The "echo=FALSE" piece keeps the code from being echoed in the output
## document- only the output will be shown
set.seed(1)
x<-rnorm(100)
mean(x)
```

```{r computetime, echo=FALSE}
time<- format(Sys.time(), "%a %b %d %X %Y")
rand<-rnorm(1)
```

The current time is `r time` 

My favorite random number is `r rand`

(Note the previous sentences used code!)

## Introduction: Incorporating Graphics

Let's first simulate some data 
```{r simulatedata, echo=TRUE}
x<-rnorm(100); y<-x+rnorm(100,sd=0.5)
```

Here is a scatterplot of the data.
```{r scatterplot, fig.height=4}
par(mar=c(5,4,1,1),las=1)
plot(x,y,main="My Simulated Data")
```


## Making Tables with xtable

We want to make a pretty table- not just a standard table
```{r fitmodel}
library(datasets)
data(airquality)
fit<-lm(Ozone~Wind+Temp+Solar.R,data=airquality)
```

Here is a table of regression coefficients.
```{r showtable,results="asis"}
library(xtable)
xt<-xtable(summary(fit))
print(xt,type="html")
```


## Setting Global Options (Do this first in your document)

This is good if you always want "echo=FALSE" or other similar things
```{r setoptions,echo=FALSE}
## opts_chunk$set(echo=FALSE,results="hide")
##Obviously uncomment if you want to use this
```

First simulate data
```{r simulatedata2, echo=TRUE}
x<-rnorm(100); y<-x+rnorm(100,sd=0.5)
```

Here is a scatterplot of the data.
```{r scatterplot2, fig.height=4}
par(mar=c(5,4,1,1),las=1)
plot(x,y,main="My Simulated Data")
```

## Caching Computations

If you have complex code chunks, this can take a long time to run so use the
option "cache=TRUE" when possible to save yourself some time (use in the chunks
themselves)